Discriminating the Influence of Correlated Factors \\from Multivariate Observations: the Back-to-Back Regression

### 2020-05-19 paper/synthetic.tex
synthetic

In our synthetic figures, we do report each feature $i$ separately, as they are
randomly generated. $\Delta R$ thus represents the average of $\Delta R_i$. A
higher score means that for prediction, the model relies on individual features
rather than combinations of features.

Figures~\ref{fig:percondition} (bottom) and \ref{fig:auc_plots} (right, in
Appendix) show that B2B outperforms baseline models.

>>>>

\subsection{Results of the synthetic experiment}

Figures~\ref{fig:percondition} (bottom) and \ref{fig:auc_plots} (right, in
Appendix) show the results of our synthetic experiment. Note that the figure
does not display each feature $i$ separately, as they are
randomly generated. $\Delta R$ represents the average of $\Delta R_i$. A
higher score means that for prediction, the model relies on individual features
rather than combinations of features. Overall both the AUC and the held-out
prediction reliability evaluations show that B2B outperforms baseline models.
